---
title: "Tutorial: Simple Graphs in R"
output: 
  learnr::tutorial:
    progressive: true
    allow_skip: true
runtime: shiny_prerendered
description: >
  This tutorial was adapted from [Frank McCown's](https://sites.harding.edu/fmccown/r/) site on simple graphs in R. 
  It will cover line, bar, dot, and pie charts, as well as histograms and some related items
---

```{r setup, include=FALSE}
library(learnr)
library(tidyverse)
library(WILD7150)
knitr::opts_chunk$set(echo = FALSE)
```


## Purpose

This tutorial was adapted from [Frank McCown's](https://sites.harding.edu/fmccown/r/) site on simple graphs in R. Once complete, students should be familiar with the **following learning objectives**:

* Line Graphs
* Bar Graphs
* Pie Graphs
* Histograms
* Dot Graphs
* Base Graph Customization

**Submission**

For lab assignment #8, use dataset #1 and dataset #2 to create graphs similar to those overviewed in this tutorial. Choose an appropriate subset of the data for the type of graph you are making. Use this week's lecture videos to render a PDF of plots from **ONE** dataset. Submit this PDF along with your response in a text file `LAST_NAME_Reflection9.txt` to the following reflection question on Canvas:

*Reflection question here, something focused on graphical representation, maybe revisiting the concepts of having the correct plot type to accurately represent the data?*

## Getting Started

This tutorial was created using R markdown and integrated with an R shiny interface for an interactive experience ([Source Code Here]()).

The interactive code blocks behave just as they would in R. If you get stuck somewhere, use the solution button for guidance!

If you have any questions, or find any issue, please let me know at adc0032@auburn.edu!

### Demo Exercise 

*Here's a simple demonstration with an empty code chunk provided for entering the answer.*

Write the R code required to add two plus two:

```{r two-plus-two, exercise=TRUE, exercise.eval=TRUE}
```

```{r two-plus-two-hint}
2 + 2
```

### Next Steps

Easy enough, right?! 

You will be using datasets borrowed from [Assignment #6](http://webhome.auburn.edu/~tds0009/WILD7150/Assignments/Assign6.html) in [Dr. Todd Steury's WILD 7150 course](http://webhome.auburn.edu/~tds0009/wild7150.html). This tutorial uses Dataset #3. For practice, go back and use Datasets #1 and #2 with the commands you've used in this tutorial to produce similar plots. 

Here's a quick look at dataset #3. This dataset contains tree height at different ages for 16 individual trees. 

```{r check_data, exercise=TRUE, exercise.eval=FALSE}
head(x = )
```
Have fun!! 
![]()

## Line Graphs

### View



Modify the following code to limit the number of rows printed to 5:

```{r print-limit, exercise=TRUE, exercise.eval=TRUE}
mtcars
```

```{r print-limit-hint}
head(mtcars)
```

### Quiz

*You can include any number of single or multiple choice questions as a quiz. Use the `question` function to define a question and the `quiz` function for grouping multiple questions together.*

Some questions to verify that you understand the purposes of various base and recommended R packages:

```{r quiz}
quiz(
  question("Which package contains functions for installing other R packages?",
    answer("base"),
    answer("tools"),
    answer("utils", correct = TRUE),
    answer("codetools")
  ),
  question("Which of the R packages listed below are used to create plots?",
    answer("lattice", correct = TRUE),
    answer("tools"),
    answer("stats"),
    answer("grid", correct = TRUE)
  )
)
```

